\begin{thebibliography}{9}
\bibitem{sourcecode} 
Codice sorgente del progetto, testbench, latex e scripts.
\href{http://github.com/doppioandante/tesi}{Link Github}.

\bibitem{midispec}
The MIDI association.
\textit{The MIDI 1.0 Specification}

\bibitem{artix7overview}
Xilinx.
\href{https://www.xilinx.com/support/documentation/data_sheets/ds180_7Series_Overview.pdf}{\textit{7 Series FPGAs Data Sheet: Overview}}.

\bibitem{artix7clb}
Xilinx.
\href{https://www.xilinx.com/support/documentation/user_guides/ug474_7Series_CLB.pdf}{\textit{7 Series FPGAs Configurable Logic Block}}

\bibitem{nexys4referencemanual} 
Digilent.
\href{https://www.xilinx.com/support/documentation/university/XUP%20Boards/XUPNexys4DDR/documentation/Nexys4-DDR_rm.pdf}{\textit{Nexys4 DDR FPGA Board Reference Manual}}
% Albert Einstein. 
% \textit{Zur Elektrodynamik bewegter K{\"o}rper}. (German) 
% [\textit{On the electrodynamics of moving bodies}]. 
% Annalen der Physik, 322(10):891–921, 1905.

\bibitem{oppenheim}
Oppenheim, Allan V. and Willsky, Alan S. and Nawab, S. Hamid
\textit{Signals \& Systems (2Nd Ed.)}.
Prenctice-Hall, Inc., 1996.

\bibitem{tlc}
Nevio, Benveuto.
\textit{Principles of Communications Networks and Systems}.
Wiley, 2011.

\bibitem{pwmspectrum}
Song, Sarwate.
\textit{The Frequency Spectrum of Pulse Width Modulated Signals}.
Signal Processing Volume 83, Issue 10, October 2003, Pages 2227-2258.

\bibitem{analogdevicessec4}
Analog Devices.
\textit{A Technical Tutorial on Digital Signal Synthesis}.
Section 4.

\bibitem{exactspurs}
Torosyan, Willson.
\textit{Exact analysis of DDS spurs and SNR due to phase truncation and arbitrary phase-to-amplitude errors}
Proceedings of the 2005 IEEE International Conference.
Frequency Control Symposium and Exposition, 2005. 
\end{thebibliography}
